Unsurprisingly, it's difficult for me to acknowledge all those who have been there in some form or another along my journey to this point. Not for spite or pride, but for brevity; there are neither enough words nor pages for me to adequately thank everyone in name or deed. I am eternally grateful for each of you, this is only a small slice thereof. 

First and foremost, I would like to thank my advisor, Andrei Gritsan. Over the past few years that I've known and worked with you, we've published a number of different results that have all taken countless shared hours, conversations, and emails. What I've learned from our talks -- either in physics, in communication skills, or in self-determination -- has been invaluable. Without your intuition, encouragement, and support, I wouldn't be where I am today. 

I must also thank all of my colleagues and collaborators in the JHU HEP group. I owe much of what has been achieved and who I have become in the last few years to you. Morris, Petar, Barry, and Bruce have each supplied words of advice and inspiration over my time at Hopkins. Yanyan, Nhan, Andrew, Sara, and Meng: your ample experience and boundless patience was a godsend. To Candice and Heshy, I feel so lucky to have worked alongside you. For Marc, Dave, Nick, Kevin, Yongjie, Alice, Raymond, and Yaofu: our debates, collective troubleshooting, and general companionship has been my sustenance. And to Chris and Ulascan, there is no earthly way these results would have made it to publication without our discussions, arguments, and sweat. Knowing that we were in this together made it not only feasible but endurable.

To those JHU colleagues now elsewhere, especially Kirill, Fabrizio, and Markus, I'm honored to have collaborated with you. For my fellow CMS members abroad, especially Roberto, Nicola, NDF, Michalis, and all the collaborators from the Higgs and ZZ4L group, your expertise and assistance has been crucial, both to myself and the field. To the administrative staff in Bloomberg -- Carm, Pam, Kelley, Brian -- I'm so grateful for everything you have done to keep this program afloat. 

To Chris, Matt, Sean, and David: your combined theoretical expertise is awe-inspiring and our various discussions -- on physics or far afield -- have been immeasurable and I'm honored to call you friends. Tristan, Kate, Grace: our adventures through these past few years are some of the most memorable experiences I've ever had and I will always treasure them. For Matt, Justin, Nik, Keith, Derek, JT, and Mike, thank you for all of the great -- occasionally inane, though nothing if not interesting -- conversations and good times we've had together. To KFC, thank you for all the  -- almost always inane -- phone calls, late nights, and arguments over the years.

Lastly, the support and understanding from my family has been my rock through troubled seas. Throughout my life, there have been periods of unease, stress, and heartbreak. And yet, I am always in awe at your resilience and limitless love. Truly, to my parents, to my siblings, to my aunts and uncles and cousins, I owe my life and who I am to you all.
Finally, to my wonderful girlfriend Nassira, I cannot imagine what my life would have been without you. That I could have been fortunate enough to meet you, to share this journey next to you, to grow with you - I feel so privileged and I can't wait to see what we do next. 