\newlength{\oldcvlabelwidth}
\newlength{\oldcvlabelsep}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\oldcvlabelsep}{\cvlabelsep}

\setlength{\cvlabelwidth}{1em}

\begin{cvlist}{Education}
\item \emph{B.S., Physics}\\
Carnegie Mellon University, September 2005 - June 2009
\item \emph{M.A., Physics}\\
Johns Hopkins University, 2011
\item \emph{Ph.D., Physics}, Expected May 2015\\
  Johns Hopkins University, September 2009 - present  
\end{cvlist}

\setlength{\cvlabelwidth}{0em}
\setlength{\cvlabelsep}{\labelsep}

\begin{small}

\begin{cvlist}{Research Experience}
\item
\begin{itemize}\itemsep=0.25em
	\item Graduate Research, Johns Hopkins University, CMS Collaboration, 2011 - present
         \begin{itemize}
		\item words
		\item words
	\end{itemize}
	\item Graduate Research, INFN Bari, CMS Collaboration, 2012
	\begin{itemize}
		\item words
	\end{itemize}
	\item Monte Carlo Convener for HZZ, CMS Collaboration, 2013 - 2014
	\begin{itemize}
		\item Organized Monte Carlo Simulation across 20+ institutions from 7 countries
		\item 
	\end{itemize}
\end{itemize}
\end{cvlist}

\begin{cvlist}{Teaching Experience}
\item
\begin{itemize}\itemsep=0.25em
	\item CMS Data Analysis School Facilitator, Fermilab, January 2013
	\begin{itemize}
		\item Organized Data Analysis Exercise for Graduate Students in CMS Collaboration
		\item 
	\end{itemize}
	\item Teaching Assistant
	\begin{itemize}
		\item General Physics I, Fall 2009 \& Spring 2011
		\item General Physics II, Spring 2010 \& Spring 2012
		\item Special Relativity and Waves, Fall 2011
		\item Advanced Physics Lab, Spring 2013 \& Spring 2014
		\item General Mechanics II, Spring 2015
	\end{itemize}
\end{itemize}
\end{cvlist}

\begin{cvlist}{Presentations and Talks}
	\item
	``Constraints on the Higgs boson total width using off-shell production in the ZZ decay", Pheno 2014. Pittsburgh, PA, May 2014.
	\item
	``Measurement of the properties of a Higgs boson in the four-lepton final state", APS April Meeting. Savannah, GA, April 2014.
	\item
	``Constraints on the Higgs boson width from off-shell $H\rightarrow ZZ$ production", CMS WGM 183. Geneva, Switzerland, April 2014.
\end{cvlist}

\begin{cvlist}{Publications}
\item
\begin{itemize}\itemsep=0.25em
	\item
	I. Anderson et al., ``Constraining anomalous HVV interactions at proton and lepton colliders", Phys. Rev. D 89, 035007 
	\item
	CMS Collaboration, ``Measurement of the properties of a Higgs boson in the four-lepton final state", Phys. Rev. D 89, 092007
	\item 
	CMS Collaboration, ``Constraints on the Higgs boson width from off-shell production and decay to Z-boson pairs", Phys. Lett. B 736 (2014) 64 
	\item
	CMS Collaboration, ``Constraints on the spin-parity and anomalous HVV couplings of the Higgs boson in proton collisions at 7 and 8 TeV", CMS PAS HIG-14-018 (2014)
	%\item
	%CMS Collaboration, ``High mass WW and ZZ Higgs search with full statistics", CMS PAS
	%\item
	%CMS Collaboration, ``Lifetime analysis using Higgs to 4l events", CMS PAS
	\end{itemize}
\end{cvlist}

\begin{cvlist}{Outreach}
\item
\begin{itemize}\itemsep=0.25em
\item "The Science of the Large Hadron Collider", USA Science and Engineering Festival, Washington D.C., USA, April 2012 and  April 2014.
\item Johns Hopkins Physics Fair, Baltimore, MD, USA, April 2010, April 2011, April 2012, and April 2015.
\item high schools
\end{itemize}
\end{cvlist}

\setlength{\cvlabelwidth}{\oldcvlabelwidth}
\setlength{\cvlabelsep}{\oldcvlabelsep}
\end{small}
